TODO (re-replication) (student) (cumulative science) (failure to replicate) 

### 2024-02-21 code/process.Rmd
poking

```{r}
d <- read_csv(here("data", "combined_data.csv")) |> 
  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
         open_data, open_materials, within_between, single_vignette)

@@

orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip(ylim=c(-1.1,2))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="effect size on original scale", x="")

smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
  coord_flip(ylim=c(-1.1,2))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

>>>>

```{r}
d <- read_csv(here("data", "combined_data.csv")) |> 
  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
         open_data, open_materials, within_between, single_vignette, name_pretty)

@@

orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="effect size on original scale", x="")

smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
  coord_flip(ylim=c(-1.1,1.5))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

### 2024-02-21 manuscript/manuscript.Rmd
poking

```{r}
d <- read_csv(here("data", "combined_data.csv")) |> 
  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
         open_data, open_materials, within_between, single_vignette, cost)

@@

  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |> arrange(Predictors) |> select(Predictors, r, p)

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex") #|> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
#cors

@@

```{r}
parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())

@@

TODO some of the error bars here don't look entirely consistent? 
<!--* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)-->

@@

#test on just one
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE)

for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)

orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip(ylim=c(-1.1,2))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="effect size on original scale", x="")

smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
  coord_flip(ylim=c(-1.1,2))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

@@

>>>>

```{r}
d <- read_csv(here("data", "combined_data.csv")) |> 
  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
         open_data, open_materials, within_between, single_vignette, cost, name_pretty)

@@

  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex") |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
#cors

@@

```{r}
parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))  |>kable_classic()

@@

TODO some of the error bars here don't look entirely consistent?

One issue with comparing on SMD scale is that noisier measures make the effect smaller even if the units are the same on the original scale. 
<!--* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)-->

@@

#test on just one
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE) 
for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)

orig_scale <- ggplot(for_plotting,aes(x=reorder(name_pretty, point, FUN=max), y,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="effect size on original scale", x="")

smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
  coord_flip(ylim=c(-1.1,1.5))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

@@

```{r}
do_d_predInt_het <- function(df){
  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
    yio=df$d
    vio=df$d_se**2
    yir=df$rep_d
    vir=df$rep_d_se**2
    t2=.21**2
    pooled.SE = sqrt(vio + vir + t2)
    PILo.sens = yio - qnorm(0.975) * pooled.SE
    PIHi.sens = yio + qnorm(0.975) * pooled.SE
    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
  }
  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
}

```{r}
orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)

predInts_het <- parsed_d |> 
  filter(type!="original") |> 
  group_by(target_lastauthor_year, name_pretty) |> 
  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
  left_join(orig) |> 
  group_by(target_lastauthor_year,type) |> 
  nest() |> 
  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
  unnest_wider(d_pred_int) |> 
  unnest_wider(data)

```{r, fig.height=6, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

 ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black", alpha=.5)+
  geom_point(aes(y=d), color="black", position=position_dodge(width=.3), shape=1, alpha=.5)+
     geom_point(size=2.5, position=position_dodge(width=.4))+

  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position="bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="predInts on SMD scale", x="")
